\headingfont UNIVERSIDAD DE EXTREMADURA\\ FACULTAD DE CIENCIAS\\[1.5cm] \textbf{ Grado en Física\\ TRABAJO DE FIN DE GRADO\\[3.5cm]} {\setstretch{1.25}\flushleft{\large{\textbf{Developement of a FIWARE-based application for tree species monitoring (dendrometry)}}\\[3.5cm]}}

### 2020-07-03 docs/LaTex/Paper.tex
Minor fixes

By other hand, in order to this sketch takes advantage of the plugged LoRa Shield, is required to base it on the LoRaMAC-in-C library \cite{MCCI_lmic} (\cmd{arduino-lmic})\footnote{Dragino has its own \href{https://github.com/dragino/arduino-lmic}{fork of this library} but has been considered less upgraded than the MCCI version, which is a fork itself from the first port of LMIC library by \href{https://github.com/matthijskooijman}{Matthijs Kooijman}.} implemented by \href{https://mcci.com/}{MCCI}, whose technical documentation can be found in \cite{MCCI_lmic_docs}. The \cmd{arduino-lmic} library is, as its description in the README.md says, a port from the IBM LoRaWAN MAC in C, but \enquote{slightly modified to run in the Arduino environment allowing using the SX1272, SX1276 transceivers and compatible modules} \cite{MCCI_lmic}. The original IBM LoRaWAN MAC in C library was developed for microcontrollers in general, their examples and HAL ---Hardware Abstraction Layer or rather Hardware Annotation Library--- were only for STM32 MCUs (but bare-metal, so no Arduino on top).

@@

As commented \href{https://github.com/mcci-catena/arduino-lmic/blob/master/examples/ttn-abp/ttn-abp.ino#L30}{lines 30 and 31} point, the most important thing before start working on the sketch is to configure the \cmd{arduino-lmic} library, so after install the library with the library manager ---in the Arduino IDE or any other chosen IDE---, the reader will need to go the library path and locate the \href{https://github.com/mcci-catena/arduino-lmic/blob/master/project_config/lmic_project_config.h}{\cmd{<lib\_path>/project\_config/lmic\_project\_config.h}} file to ensure the line 2 (\cmd{\#define CFG\_eu868 1}) is \textbf{uncommented} and the line 3 (\cmd{\#define CFG\_us915 1}) is \textbf{commented}. This is to enable specific functions in the library for Europe region (where the radio regulations are slightly different than in other regions); so this \cmd{lmic\_project\_config.h} must looks like in te example \ref{ej:lmic_project_config.h}

@@

By other hand \enquote{Any pins that are not needed should be specified as \cmd{LMIC\_UNUSED\_PIN}} as it can be also read in the \href{https://github.com/mcci-catena/arduino-lmic#pin-mapping}{Pin Mapping section} of the library \cmd{README.md}. As the reader can see, the example \ref{ej:pin_mapping} starts at line 76, that is because this is the line where the pin mapping is placed in the \href{https://github.com/WyRe/lora-arduino-dendrometer/blob/master/src/arduino/dendro/dendro.ino#L76}{written sketch}.

@@

So generating a pair of keys and configuring properly the ssh access;\footnote{The reader will probably need to figure out the Raspberry IP in their local network, by other hand, inside a local network will not be necessary specify any port for ssh, though it usually is the 22 by default.} it will probably be necessary to paste the \cmd{*.pub} key content into \cmd{~/.ssh/authorized\_keys} file (located in the local folder in the Raspberry Pi); and give it the right permissions (\cmd{700}), after this the reader should be able to connect through ssh service.

@@

Once these keys are available in TTN platform, the process can continue.

>>>>

In the other hand, in order to this sketch takes advantage of the plugged LoRa Shield, is required to base it on the LoRaMAC-in-C library \cite{MCCI_lmic} (\cmd{arduino-lmic})\footnote{Dragino has its own \href{https://github.com/dragino/arduino-lmic}{fork of this library} but has been considered less upgraded than the MCCI version, which is a fork itself from the first port of LMIC library by \href{https://github.com/matthijskooijman}{Matthijs Kooijman}.} implemented by \href{https://mcci.com/}{MCCI}, whose technical documentation can be found in \cite{MCCI_lmic_docs}. The \cmd{arduino-lmic} library is, as its description in the README.md says, a port from the IBM LoRaWAN MAC in C, but \enquote{slightly modified to run in the Arduino environment allowing using the SX1272, SX1276 transceivers and compatible modules} \cite{MCCI_lmic}. The original IBM LoRaWAN MAC in C library was developed for microcontrollers in general, their examples and HAL ---Hardware Abstraction Layer or rather Hardware Annotation Library--- were only for STM32 MCUs (but bare-metal, so no Arduino on top).

@@

As commented \href{https://github.com/mcci-catena/arduino-lmic/blob/master/examples/ttn-abp/ttn-abp.ino#L29}{lines 29 and 30} point, the most important thing before start working on the sketch is to configure the \cmd{arduino-lmic} library, so after install the library with the library manager ---in the Arduino IDE or any other chosen IDE---, the reader will need to go the library path and locate the \href{https://github.com/mcci-catena/arduino-lmic/blob/master/project_config/lmic_project_config.h}{\cmd{<lib\_path>/project\_config/lmic\_project\_config.h}} file to ensure the line 2 (\cmd{\#define CFG\_eu868 1}) is \textbf{uncommented} and the line 3 (\cmd{\#define CFG\_us915 1}) is \textbf{commented}. This is to enable specific functions in the library for Europe region (where the radio regulations are slightly different than in other regions); so this \cmd{lmic\_project\_config.h} must looks like in te example \ref{ej:lmic_project_config.h}

@@

In the other hand \enquote{Any pins that are not needed should be specified as \cmd{LMIC\_UNUSED\_PIN}} as it can be also read in the \href{https://github.com/mcci-catena/arduino-lmic#pin-mapping}{Pin Mapping section} of the library \cmd{README.md}. As the reader can see, the example \ref{ej:pin_mapping} starts at line 76, that is because this is the line where the pin mapping is placed in the \href{https://github.com/WyRe/lora-arduino-dendrometer/blob/master/src/arduino/dendro/dendro.ino#L76}{written sketch}.

@@

So generating a pair of keys and configuring properly the ssh access;\footnote{The reader will probably need to figure out the Raspberry IP in their local network, otherwise, inside a local network will not be necessary specify any port for ssh, though it usually is the 22 by default.} it will probably be necessary to paste the \cmd{*.pub} key content into \cmd{~/.ssh/authorized\_keys} file (located in the local folder in the Raspberry Pi); and give it the right permissions (\cmd{700}), after this the reader should be able to connect through ssh service.

@@

We must remember also it is so important to choose the CayenneLPP as the payload decoder. Once these keys are available in TTN platform, the process can continue.
